Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-26 Corrected_version.tex
Gros changements jusqu'à début p34

We denote by $\V^{\eps}(t)=\left(p^{\eps}(x_j,t),
u^{\eps}(x_j,t)\right)_{j\in \mathbb Z}$ the interpolation of the 
solution of the hyperbolic heat equations $P^\eps$ and by
$\V^{\eps}_h(t)=
\left(p_j^{\eps}(t), u_j^{\eps}(t)   \right)_{j\in \mathbb Z}$ the
solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
similar quantities from the diffusion scheme: it yields 
$\W^\eps(t)=\left(p(x_j,t),\varepsilon v(x_j,t)\right)_{j\in \mathbb Z}$ 
which is the interpolation of the 
solution of the diffusion limit
$P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
 and  $\W_h^\eps(t)=\left( p_j(t),  
\varepsilon v_j(t)   \right)_{j\in \mathbb Z}$ which is
the
solution of the diffusion scheme $P_h^0$ (\ref{schemadifff})-(\ref{eq:vv}). 
For simplicity we choose a final time $T>0$.
All  error estimates will be given for 
$t\leq T$, either
in the norm
$\|f(t)\|_{L^\infty([0,T];L^2(\mathbb{R}))}$, or mostly in the norm
$\|f\|_{L^2([0,T]\times \mathbb{R})}$

@@

\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
\sqrt \frac{h}\eps 
\left\| \V^{\eps}(0)
\right\|_{H^1(\mathbb{R})}.
\end{equation*}

@@

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
$\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1}) and (\ref{bee2}), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent (equation \ref{eq:initp1}) so 
 $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{t/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \bigg) ,

@@

\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{t/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \big)$. 

@@

\begin{proposition}\label{heqtode2d}
The error between the two solutions
can be  upper bounded by
\begin{equation}\label{ine3}
\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
\| \mathbf{v} 
 \|_{   L^\infty([0,T]; H^n(\Omega))  }
 \leq
C \eps
\|p_0 \|_{H^{3+n}(\Omega)},
\qquad n \in \mathbb N.
\end{equation}
\end{proposition}
\begin{proof}
The structure of the 
proof in the $L^\infty( [0,T];L^2(\Omega))$ norm is the same as the one
of proposition \ref{heqtode}.
Since the coefficients of the problem are constant, similar bounds are obtained
at any order of derivation which proves the estimate for any $n>0$.
\end{proof}

@@

Starting from (\ref{eq:4}) and taking into account of the definitions of
the fluxes (\ref{eq:5}) and also the identity $\sum_r l_{jr} \njr=0$,
the scheme $\mathbf P_h^\eps$ can also be rewritten as
\begin{equation}\label{eq:4bis}
\mathbf P_h^\eps:
\qquad
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid\frac{d}{dt} p_{j}^{\eps}+\frac{1}{\varepsilon}
\sum_{r}(l_{jr}\ur^{\eps},\njr)=0\\
\displaystyle \mid
\Omega_{j}\mid\frac{d}{dt}\uj^{\eps}+\frac{1}{\varepsilon}
\sum_{r}l_{jr} (\njr,\uu_r^{\eps} -\uu_j^{\eps})\njr=0
\end{array}
\right.
\end{equation}
When $\eps \rightarrow 0$
the scheme $\mathbf P_h^\eps$ admits the limit diffusion scheme 
$\mathbf P_h^0$ 
\begin{equation}\label{diffglace}
\mathbf P_h^0:
\qquad\left\{ \begin{array}{l}
\displaystyle \left| \Omega_j 
\right| \frac{d}{dt} p_j+ 
\sum_{r} l_{jr}\bigg( 
\vv_r,\njr\bigg)=0,\\
\displaystyle \vv_r=\frac{1}{\sigma} B_r^{-1}
\sum_{j}l_{jr}p_j\njr,
\end{array}\right.
\end{equation}
with $B_r=\sum_{j}l_{jr}\njr\otimes(\xr-\xj)$.
We  define additionally $\vv_j$ by a kind of mean
$$
\left( \sum_r \alj \right) \vv_j=\sum_r \alj
\vv_r.
$$
This is well defined since the matrix
$\sum_r \alj$ is  symetric positive by definition of the $\alj$.

\subsection{Definition of $\mathbf{DA}_h^\eps$}

@@

The characteristic length of the mesh is 
\begin{equation*} \label{eq:d6}
h=\max_j \left( \mbox{diam}(\Omega_j)  \right).
\end{equation*}
By definition  there exists  a constant $C>0$ such that 
\begin{equation} \label{eq:d7}
l_{jr}\leq Ch , \qquad \forall j,r.
\end{equation}
The control volume $V_r$ 
around the vertex $\mathbf x_r$ is 
defined by the closed loop
$
\dots, \mathbf{x}_{j-\frac12}, \mathbf{x}_j,\mathbf{x}_{j+\frac12},\dots$.
Here  the $\mathbf{x}_j$'s are the center of the cells, and the 
$\mathbf{x}_{j+\frac12}$'s are the middle of the edges around the vertices
$\mathbf{x}_r$.
A typical example is depicted in  figure \ref{figcv}.

@@

\item  The matrix $B_r$ is positive and that there exists a
constant $\alpha >0 $ independent of r such that 
\begin{equation}\label{geom3}
(B_r \uu, \uu)=(B^s_r \uu, \uu)\geq \alpha \vert
V_r\vert (\uu,\uu)
\end{equation}
where $B^s_r=\frac12 (B_r+B_r^t)$ is the symmetric part of $B_r$.
Square meshes satisfy (\ref{geom3}).
This assumption is however not trivial to check in the general case.
We point out  \cite{glaceap} where
 sufficient conditions such that (\ref{geom3}) is satisfied
can be found; in particular it is shown 
that  triangular meshes with all angles greater than $12$ degrees
satisfy it. 
\end{enumerate}
\end{hyp}

We  use the convention that the quadratic norm
of any cell centered quantity $f=(f_j)_{j\in {\rm Cells}}$ is
$\|f\|_{L^2(\Omega)}=\sqrt{\sum_j |\Omega_j| |f_j|^2   }$, while the quadratic
norm of any vertex based quantity $g=(g_r)_{r\in {\rm Vertices}}$ is
$\|g\|_{L^2(\Omega)}=\sqrt{\sum_r |V_r| |g_r|^2   }$.
Useful  quantities  are
\begin{itemize}
\item $\mathbf V_h^\eps=\left(p^\eps_j, \uu^\eps_j \right)_
{j\in {\rm Cells}}$ is the solution of $\mathbf P_h^\eps$.
\item 
$\mathbf V^\eps=\left(p^\eps(\x_j), \uu^\eps(\x_j)  \right)_
{j\in {\rm Cells}}$ is the solution of $\mathbf P^\eps$,
\item $\mathbf W_h^\eps=\left(p^\eps_j, \uu^\eps_j \right)_
{j\in {\rm Cells}}$ is the solution of $\mathbf{DA}_h^\eps$.
Notice that an abuse of notations is been made with the solution
of $\mathbf P_h^\eps$.
\item $\mathbf W^\eps= \left(p(\x_j),-\frac\eps\sigma \nabla p(\x_j)  \right)_
{j\in {\rm Cells}} $ is the solution of $\mathbf P^0$.
\end{itemize}
With these notations,  (\ref{ine3}) is rewritten as
\begin{equation} \label{eq:enc22}
\|\W^\eps-\mathbf V^\eps\|
_{ L^2([0,T]\times L^2(\Omega)   ) } \leq C \eps.
\end{equation}

@@

\begin{pro}[Stability] \label{propesti} Under the geometrical assumption (\ref{geom3}), the
semi-discrete general JL-(b) scheme defined by (\ref{eq:4},\ref{eq:5})  is
stable in the $L^2$ norm in the sense that $\frac{d}{dt}
 \vert\vert \V^{\eps}_{h}(t)
\vert\vert \leq 0$.
 Moreover we have the bounds
\begin{equation}\label{gggg}
\frac{\sigma}{\eps^2}\vert\vert \uu_r^{\eps} \vert\vert_{L^2([0,T]\times \Omega)}\leq
C 
\vert\vert
V^{\eps}_h(0)\vert\vert_{L^2( \Omega)}, \qquad C>0,
\end{equation}
\begin{equation}\label{gs}
\int_0^T\sum_j \sum_r
l_{jr}(\njr,(\uj^\eps-\ur^\eps))^{2} dt\leq C  \eps \vert\vert
\mathbf V^{\eps}_h(0)\vert\vert^2_{L^2( \Omega)}. 
\qquad C>0.
\end{equation}
\end{pro}

@@

\begin{proposition}[Convergence]\label{ein_prosit}
There exists a constant $C(T, \sigma)>0$ 
      such that the following estimate holds
\begin{equation} \label{eq:veps2}
\|\V^{\eps}_h-\V^{\eps}\|_{L^\infty( [0,T]\times L^2  (\Omega) )}\leq
C(T, \sigma)\|  \mathbf V ^\eps (0) \|_  { H^3(\Omega)  }
\sqrt{\frac h \eps}.
\end{equation}
\end{proposition}
In the whole proof, we will use a constant $C>0$ large enough.
 Like in 1D, we use the method introduced by Mazeran \cite{Mazeran}. 
We introduce
$\mathscr{E}(t)=\frac12 \|\V^{\eps}-\V^{\eps}_h\|_{L^2(\Omega)}^2$.
As for the 1D proof and for the sake of simplicity, for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $.

@@

\hspace{0.6cm}+ \frac{1}{\eps} \sum_j \sum_r \bigg(

@@

\hspace{0.6cm}+\frac{\sigma}{\eps^2} \bigg( \sum_r \sum_j

@@

\begin{pro} \label{pro:interp}
For any funtion $q$ in $ H^3(\Omega)$,   using  Sobolev embeddings,
one has the inequalities
\begin{equation}\label{}
 \vert \delta_{jr}(q) \vert
 \leq 
  C  \| q \| _{ H^1(\Omega_j) }
\end{equation}
and
\begin{equation}
\vert \widetilde \delta_{jr}(q)\vert
\leq  
  C h^{3/2}  \| q \| _{ H^3(\Omega_j) }
\end{equation}
\end{pro}

>>>>

We denote by $\V^{\eps}(t,x)=\left(p^{\eps}(x,t),
u^{\eps}(x,t)\right)$ the solution of the hyperbolic heat equations $P^\eps$ and by
$\V^{\eps}_h(t)=
\left( \sum_{j\in \mathbb Z} p_j^{\eps}(t) {1}_{\Omega_j} ,  \sum_{j\in \mathbb Z} u_j^{\eps}(t) {1}_{\Omega_j} \right)$ the solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
similar quantities from the diffusion scheme: it yields 
$\W^\eps(t,x)=\left(p(x,t),\varepsilon v(x,t)\right)$ 
which is the 
solution of the diffusion limit
$P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
 and  $\W_h^\eps(t)= \left( \sum_{j\in \mathbb Z} p_j(t) {1}_{\Omega_j} ,
\varepsilon \sum_{j\in \mathbb Z} v_j(t)  {1}_{\Omega_j} \right)$ which is
the
solution of the diffusion scheme $P_h^0$ (\ref{schemadifff})-(\ref{eq:vv}). 
For simplicity we choose a final time $T>0$.
All  error estimates will be given for 
$t\leq T$, either
in the norm
$\|f(t)\|_{L^\infty([0,T];L^2(\mathbb{R}))}$, or mostly in the norm
$\|f\|_{L^2([0,T]\times \mathbb{R})}$

@@

\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
\sqrt \frac{h}\eps 
\left\| \V^{\eps}(0)
\right\|_{H^1(\mathbb{R})}.
\end{equation*}

@@

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
$\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1}) and (\ref{bee2}), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent (equation \ref{eq:initp1}) so 
 $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{T/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } \big( \frac12 + \frac{1}{\sigma^2} \big) } \|p_0\|_{H^2(\mathbb{R})} \bigg) ,

@@

\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{T/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \big)$. 

@@

\begin{proposition}\label{heqtode2d}
The error between the two solutions
can be  upper bounded by
\begin{equation}\label{ine3}
\textcolor{red}{\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
\| \mathbf{v} 
 \|_{   L^\infty([0,T]; H^n(\Omega))  }
 \leq
C \eps
\|p_0 \|_{H^{3+n}(\Omega)},
\qquad n \in \mathbb N.}
\end{equation}
\end{proposition}
\begin{proof}
The structure of the 
proof in the $L^\infty( [0,T];L^2(\Omega))$ norm is the same as the one
of proposition \ref{heqtode}.
Since the coefficients of the problem are constant, similar bounds are obtained
at any order of derivation which proves the estimate for any $n>0$.
\end{proof}

@@

Starting from (\ref{eq:4}) and taking into account of the definitions of
the fluxes (\ref{eq:5}) and also the identity $\sum_r l_{jr} \njr=0$,
the scheme $\mathbf P_h^\eps$ can also be rewritten as
\begin{equation}\label{eq:4bis}
\mathbf P_h^\eps:
\qquad
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid\frac{d}{dt} p_{j}^{\eps}+\frac{1}{\varepsilon}
\sum_{r}(l_{jr}\ur^{\eps},\njr)=0\\
\displaystyle \mid
\Omega_{j}\mid\frac{d}{dt}\uj^{\eps}+\frac{1}{\varepsilon}
\sum_{r}l_{jr} (\njr,\uu_r^{\eps} -\uu_j^{\eps})\njr=0
\end{array}
\right.
\end{equation}
When $\eps \rightarrow 0$
the scheme $\mathbf P_h^\eps$ admits the limit diffusion scheme 
$\mathbf P_h^0$ 
\begin{equation}\label{diffglace}
\mathbf P_h^0:
\qquad\left\{ \begin{array}{l}
\displaystyle \left| \Omega_j 
\right| \frac{d}{dt} p_j+ 
\sum_{r} l_{jr}\bigg( 
\vv_r,\njr\bigg)=0,\\
\displaystyle \vv_r=\frac{1}{\sigma} B_r^{-1}
\sum_{j}l_{jr}p_j\njr,
\end{array}\right.
\end{equation}
with $B_r=\sum_{j}l_{jr}\njr\otimes(\xr-\xj)$.
We  define additionally $\vv_j$ by a kind of mean
$$
\left( \sum_r \alj \right) \vv_j=\sum_r \alj
\vv_r.
$$
This is well defined since the matrix
$\sum_r \alj$ is  symetric positive by definition of the $\alj$.
\subsection{Definition of $\mathbf{DA}_h^\eps$}

@@

The characteristic length of the mesh is 
\begin{equation*} \label{eq:d6}
h=\max_j \left( \mbox{diam}(\Omega_j)  \right).
\end{equation*}
By definition  there exists  a constant $C_{\mathcal{M}}>0$ such that 
\begin{equation} \label{eq:d7}
\left\{
\begin{aligned}
&l_{jr}\leq C_{\mathcal{M}}h , \qquad \forall j,r , \\
&|\Omega_j| \leq C_{\mathcal{M}}^2 h^2 , \qquad \forall j .
\end{aligned}
\right. 
\end{equation}
The control volume $V_r$ 
around the vertex $\mathbf x_r$ is 
defined by the closed loop
$
\dots, \mathbf{x}_{j-\frac12}, \mathbf{x}_j,\mathbf{x}_{j+\frac12},\dots$.
Here  the $\mathbf{x}_j$'s are the center of the cells, and the 
$\mathbf{x}_{j+\frac12}$'s are the middle of the edges around the vertices
$\mathbf{x}_r$.
A typical example is depicted in  figure \ref{figcv}.

@@

\item  The matrix $B_r$ is positive and there exists a
constant $\alpha >0 $ independent of r such that 
\begin{equation}\label{geom3}
(B_r \uu, \uu)=(B^s_r \uu, \uu)\geq \alpha \vert
V_r\vert (\uu,\uu)
\end{equation}
where $B^s_r=\frac12 (B_r+B_r^t)$ is the symmetric part of $B_r$.
Square meshes satisfy (\ref{geom3}).
This assumption is however not trivial to check in the general case.
We point out  \cite{glaceap} where
 sufficient conditions such that (\ref{geom3}) is satisfied
can be found; in particular it is shown 
that  triangular meshes with all angles greater than $12$ degrees
satisfy it. 
\end{enumerate}
\end{hyp}

We  use the convention that the quadratic norm
of any cell centered quantity $f=(f_j)_{j\in {\rm Cells}}$ is
$\|f\|_{L^2(\Omega)}=\sqrt{\sum_j |\Omega_j| |f_j|^2   }$, while the quadratic
norm of any vertex based quantity $g=(g_r)_{r\in {\rm Vertices}}$ is
$\|g\|_{L^2(\Omega)}=\sqrt{\sum_r |V_r| |g_r|^2   }$.
Useful  quantities  are
\begin{itemize}
\item $\mathbf V_h^\eps=\left(  \sum_{j\in Cells} p^\eps_j 1_{\Omega_j} , \sum_{j\in Cells} \uu^\eps_j  1_{\Omega_j} \right) $ is the solution of $\mathbf P_h^\eps$.
\item 
$\mathbf V^\eps=\left(p^\eps, \uu^\eps  \right)$ is the solution of $\mathbf P^\eps$,
\item $\mathbf W_h^\eps=\left(  \sum_{j\in Cells}  p^\eps_j 1_{\Omega_j} ,  \sum_{j\in Cells}  \uu^\eps_j  1_{\Omega_j}  \right) $ is the solution of $\mathbf{DA}_h^\eps$.
Notice that an abuse of notations is been made with the solution
of $\mathbf P_h^\eps$.
\item $\mathbf W^\eps= \left( p ,-\frac\eps\sigma \nabla p  \right) $ is the solution of $\mathbf P^0$.
\end{itemize}
With these notations,  (\ref{ine3}) is rewritten as
\begin{equation} \label{eq:enc22}
\|\W^\eps-\mathbf V^\eps\|
_{ L^2([0,T]\times L^2(\Omega)   ) } \leq C \eps.
\end{equation}
The initialization stage yields 
\begin{equation}\label{constant_init}
\left\{
\begin{aligned}
&\| \mathbf{V}_0 - \mathbf{V}^{\eps}_h(0)\|_{L^2(\Omega)} \leq C_0 h \|  \mathbf V ^\eps_0 \|_  { H^1(\Omega)  } ,\\
&\| \mathbf{W}_0 - \mathbf{W}^{\eps}_h(0)\|_{L^2(\Omega)} \leq C_0 h \|  \mathbf W ^\eps_0 \|_  { H^1(\Omega)  } .
\end{aligned}
\right.
\end{equation}

@@

\begin{pro}[Stability] \label{propesti} Under the geometrical assumption (\ref{geom3}), the
semi-discrete general JL-(b) scheme defined by (\ref{eq:4},\ref{eq:5})  is
stable in the $L^2$ norm in the sense that $\frac{d}{dt}
 \vert\vert \V^{\eps}_{h}(t)
\vert\vert \leq 0$.
 Moreover we have the bounds
\begin{equation}\label{gggg}
\frac{\sigma}{\eps^2}\vert\vert \uu_r^{\eps} \vert\vert_{L^2([0,T]\times \Omega)}\leq
\frac{1}{\alpha}
\vert\vert
V^{\eps}_h(0)\vert\vert_{L^2( \Omega)},
\end{equation}
\begin{equation}\label{gs}
\int_0^T\sum_j \sum_r
l_{jr}(\njr,(\uj^\eps-\ur^\eps))^{2} dt\leq \eps \vert\vert
\mathbf V^{\eps}_h(0)\vert\vert^2_{L^2( \Omega)} .
\end{equation}
\end{pro}

@@

\begin{proposition}[Convergence]\label{ein_prosit}
The following estimate holds
\begin{equation} \label{eq:veps2}
\|\V^{\eps}_h-\V^{\eps}\|_{L^\infty( [0,T]\times L^2  (\Omega) )}\leq
C \sqrt{\frac h \eps},
\end{equation}
where
\begin{equation*}
\begin{aligned}
C = \|\mathbf{V}_0^\eps\|_{H^3(\Omega)}  \sqrt{2+T+\sigma } \: \hbox{max}\bigg\{ & \:  \frac{ C_{\mathcal{M}}^2 }{2}\sqrt{\frac{P}{C_1}} \bigg( \frac1{\alpha} + PC_{\delta}^2 \bigg) \: , \: \frac{C_{\mathcal{M}}^3P}{2C_1}  , \\
&  C_{\mathcal{M}} C_{\delta} P \bigg( \frac{1+C_0^2h^2}{C_1} + C_{\delta}  + h \bigg) \: , \: C_0^2 + C_{\mathcal{M}}^2  P C_{\delta}\bigg( 1 + \frac{2C_{\mathcal{M}}^2P}{C_1\alpha} \bigg) \: \bigg\}^{\frac12} .
\end{aligned}
\end{equation*}
The constants $P$, $C_{\delta}$, $C_{\mathcal{M}}$, $\alpha$, $C_0$ and $C_1$ are defined respectively in \eqref{nbmr}, (\ref{const_delta1}-\ref{const_delta2}), \eqref{eq:d7}, \eqref{geom3}, \eqref{constant_init} and \eqref{eq:d5.2}.
\end{proposition}
In the whole proof, we will use a constant $C>0$ large enough.
 Like in 1D, we use the method introduced by Mazeran \cite{Mazeran}. 
We introduce
$\mathscr{E}(t)=\frac12 \|\V^{\eps}-\V^{\eps}_h\|_{L^2(\Omega)}^2$.
As for the 1D proof and for the sake of simplicity, for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $.

@@

&+ \frac{1}{\eps} \sum_j \sum_r \bigg(

@@

&+\frac{\sigma}{\eps^2} \bigg( \sum_r \sum_j

@@

\begin{pro} \label{pro:interp}
For any funtion $q$ in $ H^3(\Omega)$,   using  Sobolev embeddings,
one has the inequalities
\begin{equation}\label{const_delta1}
 \vert \delta_{jr}(q) \vert
 \leq 
  C_{\delta}  \| q \| _{ H^1(\Omega_j) }
\end{equation}
and
\begin{equation}\label{const_delta2}
\vert \widetilde \delta_{jr}(q)\vert
\leq  
  C_{\delta} h^{3/2}  \| q \| _{ H^3(\Omega_j) }
\end{equation}
\end{pro}
